Bipartite Fidelity and Loschmidt Echo of Bosonic Conformal Interface

### 2017-10-10 reply_to_referee.tex

For the fidelity, one maps in Fig. 5 the initial strip to an annulus with inner and outer radii determined by the length of the strip which goes to infinity. Then one moves the point, where the boundary condition changes, to the origin, which means that, in the strip, it is moved to the far left and disappears there. I cannot see, how the calculation then proceeds. In [25], a different conformal map was used.

\reply{
We have added more descriptions in the text around Fig.5 and Fig.6 about the conformal mappings used there. One major change is Fig 5. We do not impose IR regulator(previously a vertical line at $x = W$)  on the left panel of the slit diagram, but do add the small semi-circle. After doing the conformal mapping to the center diagram, we end up with a truncated corner centered at $z = 1$. To evaluate this diagram, we add another semi-circle centered at $z = 1$ with radius $R$. This should avoid the problem the referee was worried about.

(By the way, we add the semi-circle manually in the center of Fig. 5, which is in close analogy to the computation of the truncated cone and corner in the Cardy-Peschel paper. So to get the correct result, we should subtract its contribution to the free energy, which is exactly what we do in App. C.)

The annulus diagrams in both Fig. 5 and Fig. 6 are \rev{not} strictly concentric to higher order corrections of $\frac{\epsilon}{L}, \frac{\epsilon}{\tau}$. To resolve this problem, (and maybe the worry the referee previously had), we notice the following fact
\begin{itemize}
\item the non-conformal mapping from the non-concentric circles to the cylinder diagram exists: this can be doing by first mapping the non-concentric circles to concentric circles and then use the $\ln z$ map. 
\item the resulting width of the cylinder only depend on the cross ratio of the intersection points of the two circles w.r.t. the real axis.  \rev{still don't get why the map is non-conformal}
\end{itemize}
since the conformal mapping preserve the cross ratio, we can calculate the width of the cylinder in terms of the cross ratio in the non-concentric circles. The calculation we did use the first order approximation of the cross ratio, but is enough to get the leading order of the width of the cylinder correct. The higher order corrections are of order $\frac{\epsilon}{L}$ and $\frac{\epsilon}{\tau}$, which should not affect the power law scalings of the fidelity and echo.

@@

\reply{We take this identification because the boundary state computation is easier.

In fact, since the distance between the blue lines ($\sim \ln L , \ln \tau$) on the $w$ plane in Fig.6 is much larger than the distance between the two dashed lines, one can view rotate this cylinder diagram and consider an evolution between the blue lines. This is the point of view taken by our alternative approach (an $S$ modular transformation to the figure in the boundary state calculation), the leading term of free energy is then the groundstate energy of the Hamiltonian given the boundary conditions on the dashed line, multiply by $\beta$, see Eq.(B8).

If one impose different boundary conditions on the blue lines, the free energy then is not 
\begin{equation}
F = - \ln \text{tr}( e^{ - \beta H_{ab} } ) =  \beta  E_c
\end{equation}
but (for large $\beta$ as is the case here)
\begin{equation}
\begin{aligned}
F &= - \ln \langle \text{blue boundary state 1} | e^{ - \beta H_{ab}} | \text{blue boundary state 2} \rangle \\
&= \beta  E_c - \ln \langle \text{blue boundary state 1} | \text{ground state} \rangle \\
 &\quad - \ln \langle \text{blue boundary state 2} |\text{ ground state }\rangle                                                                                 
\end{aligned}
\end{equation}
where the additional terms can be viewed as Affleck-Ludwig boundary entropy that is subleading (independent of $\beta$) in the free energy.

As far as the leading order (in beta) is concerned, the boundary conditions imposed on the blue line shouldn‚Äôt matter. We therefore take the simplest periodic boundary condition for the ease of computation. \rev{Do we want to mention this somewhere in the text?}}

@@

(6) A number of equations expressing these changes of boundary conditions appear several times in identical form: (22),(37),(40); (24),(30) and Fig.7; (18),(26),(32),(38) and Fig.8; (28),(34) and Fig.9; (36),(39) and Fig.10. This is a redundancy which should be reduced.

\reply{Question (5) and (6) are about the notations of boundary conditions.

We remove the redundant boundary condition c in the some of the equations as long as it is equal to a. The simplified notation like $\text{DN} \rightarrow \lambda$ is better to be perceived as a single boundary condition changing process and the associated bcc operator.

Since the notation is shortened, we don'Äôt let them occupy a single equation and instead put them inside a sentence. We believe that such redundancy can be tolerated given that the length of the this notation is comparable to the citation phrase in Eq.(XX)Äù, and the time it saves to look up. }

@@

But it is totally our fault not to check the number of references before submission. We have fixed it in this submission. }

(8) At no point could I see a remark on the analytical continuation from imaginary to real time. Instead, the notation changes back and forth between t and tau.

\reply{This point should be clarified in the introduction of the path-integral formalism(Sec. III. A.). All the path-integral spacetime diagrams are in the imaginary time. We only do analytic continuation to the final results of the imaginary time diagram.

We talk about the analytic continuation procedure between Eq.(16) and Fig.4 and demonstrate in Eq. (17). Thereafter we uniformly use $t$ towards the end of the main text. \rev{This seems not to be the case.. Do we want to change that?}}

@@

- There is no (a) and (b) in Figs. 8 and 9, but in the caption these are referred to.

\reply{We have modified Fig. 8 and 9 accordingly.}

- The system sizes in the numerics given in the captions are unclear to me. What does 30k or 35k mean? In Fig. 7, it says k=1 immediately after that. Is this the same k? If not, what is it? As with L, I think that such numbers should also appear in the text. If one is talking about 35.000 sites, one wonders why such a large number was taken.

\reply{The k in the math mode font is the spring constant, while the $k$ after 30 and 35 means 1000. We didn't realize the conflict. We have changed 30k to 30000 and 35k to 35000. We take 35000 sites for reducing the finite size effect in Fig. 8 which is important for the theta value near zero. }

- Fig. 11 corresponds to the right piece of Fig. 6, but is rotated by 90¬∞. This is confusing, in particular since the corresponding Fig. 12 is not rotated. The lambda line on the left has to be dotted. Also confusing is the use of x and L in (E1) below.

\reply{We didn't realize that the spatial coordinate $x$ and $x = \frac{\theta}{pi}$ have a conflict. We rotate the figure to use $y$ as coordinate and reserve $x = \frac{\theta}{pi}$. }

@@

App. A is the calculation for the main analytic results. The reader shall only need this appendix to reproduce Eq.(23).

App. B/C are supplements to analytic results. Other appendices are for the numerical models and calculational details. We have also mentioned these structural changes in the end of the introduction.}

6) The last sentence before Sec. 4 states that the analytical (incorrect) and numerical curves "merge" at theta=0. In fact, these two curves are quite different and clearly the analytical curve cannot reproduce the numerics at all, as expected. To me it seems like that the green curve coincides with the dots in Fig. 10 only by chance. I'm not sure what the relevance of this curve is or mentioning that at theta=0 the numerics and the (incorrect) analytics "merge." This merging is simply because theta=0 is the no-quench point, when the pre- and post-quench setup is the same.

\reply{We have remove the sentence of ``merging'' at theta = 0. That is as the referee said only a calibrating point. But we do want to reserve the green curve as we (subjectively) believe the collapse is not a coincidence. The difference $1/8$õ is a magic number that is twice of the majorana operator dimension, maybe indicating the structure of the 3-point function (the bcc operators between each pair of  a, b, c). We didn't write this speculation for the lack of evidence but do want to reveal this coincidence to inspire the readers.}

### 2017-10-10 analy_eval.tex
[review] 1. The part on conformal map reviewed, with one reference added (No worry, Stephan's light-cone paper is still at 25)
2. All the highlights removed except two places, one for the above, the other at the numerical.

3. One typo at App. A fixed.

4. Various places at the reply_to_referee highlighted, which need to be clarified.

For the fidelity case, the regulators as well as the conformal mappings are depicted in Fig.~\ref{fig:fidel-map}. 
\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{fig_fidel-map.pdf}
\caption{Mapping from a strip to the upper half plane $\xi  = \exp( \frac{\pi z}{L} ) $. The two black dots represent possible locations of boundary condition changing (bcc) operators. The dot inside the blue semi-circle is at coordinate $z = 1$, which is the image of the point connecting $a$ and $b$ boundaries. The other dot is at $z = 0$ and corresponds to the connection between $a$ and $c$ boundaries at $- \infty$. To evaluate the diagram, we add the outer blue semi-circle centered at $z = 1$ to be the IR cut-off and map it to the cylinder with $w = \ln(z - 1)$}
\label{fig:fidel-map}
\end{figure}
We add a small blue semi-circle to the folded strip in Fig.~\ref{fig:fidel} as the UV regulator and map it to the upper half plane using $\xi  = \exp( \frac{\pi z}{L} )$. Then both of $z = 0$ and $1$ can host bcc operators. We assume $a = c$ such that there is only one bcc operator on the real axis enclosed by the blue semi-circle at $z = 1$. In order to evaluate this diagram, we add another semi-circle centered at $z = 1$ with radius $R_{\xi}$ (this will introduce a correction as explained in App.~\ref{app:F_correction}), and map it to the cylinder diagram on the right by $w = \ln ( z- 1)$. Finally the cylinder diagram can be viewed as path integral amplitude between the boundary state $b$ and $a$
\begin{equation}
Z_{ab} = \langle a | e^{-\pi H } |b \rangle
\end{equation}

The height of the cylinder is $\pi$. The two end points of the $\epsilon$ radius semi-circle on the $z$ plane are mapped to
\begin{equation}
\exp( \pm \pi \frac{\epsilon}{ L}  ) \sim 1 \pm \pi \frac{\epsilon}{L} .
\end{equation}
The bigger blue semi-circle intersects the real axis at $1 \pm R_{\xi}$. So the width of the cylinder is 
\begin{equation}
\label{eq:fidel_cyd_width}
\ln R_{\xi} - \ln \frac{\pi \epsilon}{L} = \ln L + \text{constant} 
\end{equation}

@@

The height of the cylinder is still $\pi$ because of folding. In the $\xi$ plane, the two end points of the small semi-circle are at $\frac{\pm \epsilon}{ \tau \pm \epsilon} \sim \frac{\pm \epsilon}{ \tau }$. The end points of the larger semi-circle are at $\pm \frac{\tau \pm \epsilon}{\epsilon} \sim \frac{\pm \tau}{\epsilon}$. Hence the width of the cylinder is
\begin{equation}
\label{eq:echo_cyd_width}
\ln \frac{\tau}{\epsilon} - \ln \frac{\epsilon}{\tau } = 2 \ln \tau + \text{constant} 
\end{equation}

\begin{figure}[htb]
\centering
\includegraphics[width=\columnwidth]{fig_H-tau_fold}
\caption{Left: Diagram of Loschmidt echo that reduces to a partition function, where imaginary time is the horizontal direction, the dashed (solid) lines are open (gluing) boundary conditions. Red arrows are the directions of Hamiltonian flow that propagates the dashed line boundary state to the solid line boundary state. The blue semi-circles of radius $\epsilon$ are the UV regulators and they are identified as periodic boundaries in the direction perpendicular to the red arrow (equal time slice). Middle: Image of the map $\xi = \frac{z}{\tau - z}$. {\color{red}The two semi-circles have radii $({\tau}/{\epsilon})^{\pm1}$ respectively.}  Right: Image of $w = \ln \xi$. It is a cylinder by identifying the blue lines and the standard radial quantization procedure can be applied. }
\label{fig:H-tau_fold}
\end{figure}

One subtlety of the above description is that the two semi-circles in the center diagrams of Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold} are not precisely concentric. This can be resolved by the following observation. There exists conformal mappings from the non-concentric circles to two standard concentric circles of radii $1$ and $R$ ($R>1$) on the $\zeta$ plane. Then the logarithmic map $w = \ln \zeta$ produces a cylinder of width $\ln R$. In fact, the width of the cylinder is a conformal invariant and only depend on the cross ratio of the half annulus. The four intersection points of two standard concentric circles on $\zeta$ plane are $(\pm 1,0)$ and $(\pm R,0)$, whose cross ratio is
\begin{equation}
\eta = \frac{(1 + R)^2}{(1 - R)^2}. 
\end{equation}
Hence the width of the cylinder is $\ln \frac{\sqrt{ \eta } - 1}{\sqrt{ \eta} + 1}$. Since conformal transformation preserves the cross ratio, this is also the result if just plug in the cross ratio of the slightly non-concentric diagrams of Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold}. The calculation in Eq.~\eqref{eq:fidel_cyd_width} and Eq.~\eqref{eq:echo_cyd_width} equivalently used the leading order approximation to $\eta$ in the respective geometry and thus get the leading order term in the width of the cylinder. The slight deviation to the precise concentric geometry will only bring $\frac{\epsilon}{L}, \frac{\epsilon}{\tau}$ corrections to the width parameter and will not affect the fidelity and echo exponents.

@@

As analyzed in Sec.~\ref{sec:analytic_numerics}, $S_2( \theta)$ interpolates between DD and NN, $S_1( \theta )$ interpolates between DN and ND. In the region accessible to the numerical calculation in the lattice model, we choose the process ${\rm DD} \rightarrow  \lambda$ to verify
\begin{equation}
\label{eq:result_DDDD}
\mathcal{F} = 
\left\lbrace
\begin{aligned}
\frac{1}{8}\ln L  &\quad\text{fidelity}  \\
\frac{1}{4}\ln t   &\quad \text{echo} .  \\
\end{aligned} \right.  
\end{equation}
The same results have already been obtained for $\lambda = {\rm P}$\cite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014}. Another process \rev{$\rm{DN} \rightarrow \lambda$} {\iffalse \color{red} in Eq.~\eqref{eq:DNDN}\fi} is used to verify
\begin{equation}
\label{eq:result_DNDN}
\mathcal{F} = 
\left\lbrace
\begin{aligned}
 (x - x^2 )\ln L   &  \quad {\rm fidelity} \\
 2(x - x^2 ) \ln t  & \quad \text{ Loschmidt echo} , \\
\end{aligned} \right. 
\end{equation}
where $\lambda = \tan \theta$ and $x = \frac{\theta}{\pi}$.

>>>>

\rev{Tian ci: Proofread this part for the conformal map}

For the fidelity case, the regulators as well as the conformal mappings are depicted in Fig.~\ref{fig:fidel-map}. 
\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{fig_fidel-map.pdf}
\caption{Mapping from a strip to the upper half plane $\xi  = \exp( \frac{\pi z}{L} ) $. The two black dots represent possible locations of boundary condition changing (bcc) operators. The dot inside the blue semi-circle is at coordinate $\xi = 1$, which is the image of the point connecting $a$ and $b$ boundaries. The other dot is at $\xi = 0$ and corresponds to the connection between $a$ and $c$ boundaries at $- \infty$. To evaluate the diagram, we add the outer blue semi-circle centered at $\xi = 1$ to be the IR cut-off and map it to the cylinder with $w = \ln(\xi - 1)$}
\label{fig:fidel-map}
\end{figure}
We add a small blue semi-circle to the folded strip in Fig.~\ref{fig:fidel} as the UV regulator and map it to the upper half plane using $\xi  = \exp( \frac{\pi z}{L} )$. Then both of $\xi = 0$ and $1$ can host bcc operators. We assume $a = c$ such that there is only one bcc operator on the real axis enclosed by the blue semi-circle at $\xi = 1$. In order to evaluate this diagram, we add another semi-circle centered at $\xi = 1$ with radius $R_{\xi}$ (this will introduce a correction as explained in App.~\ref{app:F_correction}), and map it to the cylinder diagram on the right by $w = \ln ( \xi- 1)$. Finally the cylinder diagram can be viewed as path integral amplitude between the boundary state $b$ and $a$
\begin{equation}
Z_{ab} = \langle a | e^{-\pi H } |b \rangle.
\end{equation}

The height of the cylinder is $\pi$. The two end points of the $\epsilon$ radius semi-circle on the $z$ plane are mapped to
\begin{equation}
\exp( \pm \pi \frac{\epsilon}{ L}  ) \sim 1 \pm \pi \frac{\epsilon}{L} .
\end{equation}
The bigger blue semi-circle intersects the real axis at $1 \pm R_{\xi}$. So the width of the cylinder is 
\begin{equation}
\label{eq:fidel_cyd_width}
\ln R_{\xi} - \ln \frac{\pi \epsilon}{L} = \ln L + \text{constant}.
\end{equation}

@@

The height of the cylinder is still $\pi$ because of folding. In the $\xi$ plane, the two end points of the small semi-circle are at $\frac{\pm \epsilon}{ \tau \mp \epsilon} \sim \frac{\pm \epsilon}{ \tau }$. The end points of the larger semi-circle are at $\mp \frac{\tau \pm \epsilon}{\epsilon} \sim \frac{\mp \tau}{\epsilon}$. Hence the width of the cylinder is
\begin{equation}
\label{eq:echo_cyd_width}
\ln \frac{\tau}{\epsilon} - \ln \frac{\epsilon}{\tau } = 2 \ln \tau + \text{constant}.  
\end{equation}

\begin{figure}[htb]
\centering
\includegraphics[width=\columnwidth]{fig_H-tau_fold}
\caption{Left: Diagram of Loschmidt echo that reduces to a partition function, where imaginary time is the horizontal direction, the dashed (solid) lines are open (gluing) boundary conditions. Red arrows are the directions of Hamiltonian flow that propagates the dashed line boundary state to the solid line boundary state. The blue semi-circles of radius $\epsilon$ are the UV regulators and they are identified as periodic boundaries in the direction perpendicular to the red arrow (equal time slice). Middle: Image of the map $\xi = \frac{z}{\tau - z}$. The two semi-circles have radii $({\tau}/{\epsilon})^{\pm1}$ respectively.  Right: Image of $w = \ln \xi$. It is a cylinder by identifying the blue lines and the standard radial quantization procedure can be applied. }
\label{fig:H-tau_fold}
\end{figure}

One subtlety of the above description is that the two semi-circles in the center diagrams of Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold} are not precisely concentric. This can be resolved by the following observation. There exists conformal mappings $\zeta(\xi)$ that map the non-concentric circles to two standard concentric circles of radii $1$ and $R$ ($R>1$) on the $\zeta$ plane\cite{brown_complex_2009}. Then the logarithmic map $w = \ln \zeta$ produces a cylinder of width $\ln R$. In our case, the width of the cylinder is a conformal invariant that only depends on the cross ratio of the half annulus. The four intersection points of two standard concentric circles on $\zeta$ plane are $(\pm 1,0)$ and $(\pm R,0)$, whose cross ratio is
\begin{equation}
\eta = \frac{(1 + R)^2}{(1 - R)^2}. 
\end{equation}
Hence the width of the cylinder is $\ln \frac{\sqrt{ \eta } - 1}{\sqrt{ \eta} + 1}$. Since conformal transformation preserves the cross ratio, the result is the same if we use the cross ratio of the slightly non-concentric diagrams of Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold}. The calculation in Eq.~\eqref{eq:fidel_cyd_width} and Eq.~\eqref{eq:echo_cyd_width} equivalently used the leading order approximation to $\eta$ in the respective geometry and thus get the leading order term in the width of the cylinder. The slight deviation to the precise concentric geometry will only bring $\frac{\epsilon}{L}, \frac{\epsilon}{\tau}$ corrections to the width parameter and will not affect the fidelity and echo exponents.

@@

As analyzed in Sec.~\ref{sec:analytic_numerics}, $S_2( \theta)$ interpolates between DD and NN, $S_1( \theta )$ interpolates between DN and ND. In the region accessible to the numerical calculation in the lattice model, we choose the process ${\rm DD} \rightarrow  \lambda$ to verify
\begin{equation}
\label{eq:result_DDDD}
\mathcal{F} = 
\left\lbrace
\begin{aligned}
\frac{1}{8}\ln L  &\quad\text{fidelity}  \\
\frac{1}{4}\ln t   &\quad \text{echo} .  \\
\end{aligned} \right.  
\end{equation}
The same results have already been obtained for $\lambda = {\rm P}$\cite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014}. Another process $\rm{DN} \rightarrow \lambda$ {\iffalse \color{red} in Eq.~\eqref{eq:DNDN}\fi} is used to verify
\begin{equation}
\label{eq:result_DNDN}
\mathcal{F} = 
\left\lbrace
\begin{aligned}
 (x - x^2 )\ln L   &  \quad {\rm fidelity} \\
 2(x - x^2 ) \ln t  & \quad \text{ Loschmidt echo} , \\
\end{aligned} \right. 
\end{equation}
where $\lambda = \tan \theta$ and $x = \frac{\theta}{\pi}$.

### 2017-10-10 conclusion.tex
[referee] 1. answer all the referee questions. 2. make major changes in analytic solution, App. C 3. proof read the whole article
[review] 1. The part on conformal map reviewed, with one reference added (No worry, Stephan's light-cone paper is still at 25)
2. All the highlights removed except two places, one for the above, the other at the numerical.

3. One typo at App. A fixed.

4. Various places at the reply_to_referee highlighted, which need to be clarified.

We began by classifying the boundary states by two types of $S$ matrices $S_1(\theta)$ and $S_2(\theta)$, where the parameter $\theta$ -- the scattering angle -- is determined by the transmission coefficient of the interface. The conventional `DD', `NN' boundary conditions belong to special choice of $\theta$ in $S_1$ and  `DN' and P belongs to $S_2$. Generic value of $\theta$ then interpolates between those conventional boundary conditions. A harmonic chain model allows us to realize part of these partially-transmitive boundary conditions in a concrete lattice setting.

The dynamical behavior of the Loschmidt echo reflects the change of the conformal interface during the process described in {\color{red}Eq.~\eqref{eq:S_i_S_j}}.
%, which we denote as
%\begin{equation}
%S_i( \theta_1 ) \rightarrow S_j( \theta_2 )  \quad i, j = 1, 2. 
%\end{equation}
Its power law decay exponent is related to the scaling dimension of the bcc operator that mediates these interfaces. Analytic computation shows that the exponent is always $\frac{1}{4}$ when the change of boundary condition is made between different types of $S$ matrices ($i \ne j$), regardless of the choice of $\theta$. On the other hand, the exponent depends on the difference of angles $\theta_1 - \theta_2$ as a quadratic relation when the change is made between the same types of $S$ matrices ($i = j$).

>>>>

We began by classifying the boundary states by two types of $S$ matrices $S_1(\theta)$ and $S_2(\theta)$, where the parameter $\theta$ -- the scattering angle -- is determined by the transmission coefficient of the interface. The conventional `DD', `NN' boundary conditions belong to the special choice of $\theta$ in $S_1$, and `DN' and P are among the special choices of $S_2$. Generic value of $\theta$ then interpolates between those conventional boundary conditions. A harmonic chain model allows us to realize part of these partially-transmitive boundary conditions in a concrete lattice setting.

The dynamical behavior of the Loschmidt echo reflects the change of the conformal interface during the process described in Eq.~\eqref{eq:S_i_S_j}.
%, which we denote as
%\begin{equation}
%S_i( \theta_1 ) \rightarrow S_j( \theta_2 )  \quad i, j = 1, 2. 
%\end{equation}
Its power law decay exponent is related to the scaling dimension of the bcc operator that mediates these interfaces. Analytic computation shows that the exponent is always $\frac{1}{4}$ when the change of boundary condition is made between different types of $S$ matrices ($i \ne j$), regardless of the choice of $\theta$. On the other hand, the exponent depends on the difference of angles $\theta_1 - \theta_2$ as a quadratic relation when the change is made between the same types of $S$ matrices ($i = j$).

### 2017-10-10 def_fidel_echo.tex
[review] 1. The part on conformal map reviewed, with one reference added (No worry, Stephan's light-cone paper is still at 25)
2. All the highlights removed except two places, one for the above, the other at the numerical.

3. One typo at App. A fixed.

4. Various places at the reply_to_referee highlighted, which need to be clarified.

The Loschmidt echo is also the (square of the) overlap of two wavefunctions. One of the them is the groundstate of the disconnected chains and the other is the groundstate evolved by the Hamiltonian of the connected chains
\begin{equation}
\mathcal{L}( t )  \equiv |\langle \psi_{\rm gnd}  | e^{-i H t } | \psi_{\rm gnd} \rangle|^2 .
\end{equation}
\rev{The imaginary time version $\mathcal{L}( \tau  ) = |\langle \psi_{\rm gnd}  | e^{-H \tau } | \psi_{\rm gnd} \rangle|^2$ has a path integral definition} similar to Fig.~\ref{fig:cut-and-join}, but to be consistent with the fidelity diagram, we take the horizontal axis as imaginary time and present it in Fig.~\ref{fig:echo}. Viewing the diagram as a partition function subject to the switching of boundary conditions, the logarithmic Loschmidt echo is also the associated free energy. \rev{After obtaining the free energy in imaginary time, we can analytically continue back to real time and get the $t$ dependence. For simplicity and comparison with the fidelity result, we will take the length of both of the chains to be $L$ and set $L \gg t$, leaving $t$ the only length scaling in the echo calculation (Fig.~\ref{fig:H-tau_fold}). The dependence on nonzero $\frac{t}{L}$ and the asymmetry of the lengths of the chains will not be discussed here (see their treatment in Ref.~\onlinecite{stephan_local_2011} for special values of $\lambda$).}

@@

If the interface is completely transparent, i.e. at the special point of $\lambda = 1$, the tip of the slit can be regarded as a corner singularity. According to Cardy and Peschel\cite{cardy_finite-size_1988}, the singularity will contribute to a term that is logarithmic of the corner's characteristic size, which is $\ln L$ in fidelity and $\ln \tau$ in Loschmidt echo. One would expect the fidelity and echo to have power law decay with respect to these scales in the long wavelength limit. In fact, the computations have been done in Ref.~\onlinecite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014} using either the Cardy-Peschel formula or integration of the Ward identity. If the slits boundary conditions are taken to be Dirichlet, we have the universal behavior for the leading term \cite{stephan_logarithmic_2013,stephan_local_2011}
\begin{equation}
\label{eq:full-pass}
\begin{aligned}
  \mathcal{F}({\rm fidelity}) &=  \frac{c}{8} \ln L \\
 \mathcal{F}( {\rm echo} )  &= \frac{c}{4} \ln |\tau| \rightarrow \frac{c}{4} \ln |it + \epsilon|   \sim \frac{c}{4}\ln t ,
\end{aligned}
\end{equation}
\rev{where we have performed analytic continuation $\tau \rightarrow it + \epsilon$ with $\epsilon \rightarrow 0$ for echo}.

With the presence of the conformal interface, the tip of the slit is no longer a {\color{red}corner singularity\cite{cardy_finite-size_1988}} . Its nature is clearer in the folding picture shown in Fig.~\ref{fig:fidel} and Fig.~\ref{fig:echo} where the lower half plane is flipped up on top of the upper half plane on both fidelity and echo diagram. From the boundary CFT point of view, the change of boundary condition can be regarded as inserting a primary field which is a bcc operator. The diagrams for fidelity and echo then become the one point or two point functions of the bcc operators respectively, and the free energy logarithmic term extracts their scaling dimensions.

>>>>

The Loschmidt echo is also the (square of the) overlap of two wavefunctions. One of the them is the groundstate of the disconnected chains and the other is the groundstate evolved by the Hamiltonian of the connected chains
\begin{equation}
\mathcal{L}( t )  \equiv |\langle \psi_{\rm gnd}  | e^{-i H t } | \psi_{\rm gnd} \rangle|^2 .
\end{equation}
The imaginary time version $\mathcal{L}( \tau  ) = |\langle \psi_{\rm gnd}  | e^{-H \tau } | \psi_{\rm gnd} \rangle|^2$ has a path integral definition similar to Fig.~\ref{fig:cut-and-join}, but to be consistent with the fidelity diagram, we take the horizontal axis as imaginary time and present it in Fig.~\ref{fig:echo}. Viewing the diagram as a partition function subject to the switching of boundary conditions, the logarithmic Loschmidt echo is also the associated free energy. After obtaining the free energy in imaginary time, we can analytically continue back to real time and get the $t$ dependence. For simplicity and comparison with the fidelity result, we will take the length of both of the chains to be $L$ and set $L \gg t$, leaving $t$ the only length scaling in the echo calculation (Fig.~\ref{fig:H-tau_fold}). The dependence on nonzero $\frac{t}{L}$ and the asymmetry of the lengths of the chains will not be discussed here (see their treatment in Ref.~\onlinecite{stephan_local_2011} for special values of $\lambda$).

@@

If the interface is completely transparent, i.e. at the special point of $\lambda = 1$, the tip of the slit can be regarded as a corner singularity. According to Cardy and Peschel\cite{cardy_finite-size_1988}, the singularity will contribute to a term that is logarithmic of the corner's characteristic size, which is $\ln L$ in fidelity and $\ln \tau$ in Loschmidt echo. One would expect the fidelity and echo to have power law decay with respect to these scales in the long wavelength limit. In fact, the computations have been done in Ref.~\onlinecite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014} using either the Cardy-Peschel formula or integration of the Ward identity. If the slits boundary conditions are taken to be Dirichlet, we have the universal behavior for the leading term \cite{stephan_logarithmic_2013,stephan_local_2011}
\begin{equation}
\label{eq:full-pass}
\begin{aligned}
  \mathcal{F}({\rm fidelity}) &=  \frac{c}{8} \ln L, \\
 \mathcal{F}( {\rm echo} )  &= \frac{c}{4} \ln |\tau| \rightarrow \frac{c}{4} \ln |it + \epsilon|   \sim \frac{c}{4}\ln t ,
\end{aligned}
\end{equation}
where we have performed analytic continuation $\tau \rightarrow it + \epsilon$ with $\epsilon \rightarrow 0$ for echo.

With the presence of the conformal interface, the tip of the slit is no longer a corner singularity\cite{cardy_finite-size_1988} . Its nature is clearer in the folding picture shown in Fig.~\ref{fig:fidel} and Fig.~\ref{fig:echo} where the lower half plane is flipped up on top of the upper half plane on both fidelity and echo diagram. From the boundary CFT point of view, the change of boundary condition can be regarded as inserting a primary field which is a bcc operator. The diagrams for fidelity and echo then become the one point or two point functions of the bcc operators respectively, and the free energy logarithmic term extracts their scaling dimensions.
